---
title: "Additional Analysis"
---


###Assoiciations Between Crime and Income/Unemployment
```{r, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, collapse = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(rvest)
library(httr)
library(janitor)
library(lubridate)
library(readxl)
library(plotly)
library(forcats)
library(stringr)
library(gridExtra)
library(grid)
library(ggpubr)
library(tidytext)
theme_set(theme_bw())

nyc_crime_2017 = read_csv("./report/NYPD_Complaint_Data_Current_YTD.csv") %>%
  clean_names()

nyc_crime_2017 = nyc_crime_2017 %>%
  mutate(cmplnt_fr_dt = as.Date(cmplnt_fr_dt, "%m/%d/%Y")) %>%
  select(cmplnt_fr_dt, cmplnt_fr_tm, ky_cd, ofns_desc, law_cat_cd, boro_nm, prem_typ_desc, longitude, latitude) %>%
  filter(year(cmplnt_fr_dt)  == 2017) %>%
  rename(date = cmplnt_fr_dt, time = cmplnt_fr_tm, prem_typ = prem_typ_desc, ofns_type = law_cat_cd, boro = boro_nm)
```


```{r, include = FALSE}
nyc_crime = read_csv("./report/NYPD_Complaint_Data_Current_YTD.csv") %>%
  clean_names() %>%
  select(boro = boro_nm)

crime_number = nyc_crime %>%
  group_by(boro) %>%
  summarise(n = n()) 

population = read_csv("./report/NYC_Population_by_Borough.csv") %>%
  mutate(boro = Borough) %>%
  select(-Borough)

nyc_crime_population = left_join(population, crime_number, by = "boro") %>%
  clean_names() %>%
  mutate(population = as.numeric(population)) %>%
  mutate(crime_rate = n / population * 100000)
```

```{r, echo = FALSE}
income = read_csv("./report/NYC_Income_by_Borough.csv") %>%
  clean_names() %>%
  mutate(boro = borough) %>%
  select(-borough)

crime_income = left_join(income, nyc_crime_population, by = "boro")

crime_income_plot = crime_income %>%
  ggplot(aes(x = income, y = crime_rate, fill=boro)) + geom_bar(stat="identity") +
  labs(title = "Crime Rate against Median Income",
       x = "Income Range",
       y = "Crime rate")
```

```{r, include = FALSE}
unemployment_rate = read_excel("./report/BoroMonth.xls", skip = 3) %>%
  clean_names() %>%
  select(boro, unemployment) %>%
  mutate(unemployment_rate = unemployment) %>%
  select(-unemployment)

unemployment_crime = left_join(unemployment_rate, nyc_crime_population, by = "boro")
```

```{r,include=FALSE}
unemployment_crime_plot = unemployment_crime %>%
  ggplot(aes(x = unemployment_rate, y = crime_rate, fill = boro)) + geom_bar(stat="identity") +
  labs(title = "Crime Rate against Unemployment",
       x = "Unemployment rate",
       y = "Crime rate")

```


```{r,echo=FALSE}
ggarrange(crime_income_plot, unemployment_crime_plot, ncol = 2, common.legend = TRUE)
```

* We choose household income level by borough. According to the results, both lower-income borough Bronx and higher-income borough Manhattan have the highest crime rate. Middle-income boroughs are associated with lower crime rate.

* Let unemployment rate by borough be another potential indicator. From the results, all boroughs prove a positive correlation between unemployment rate and crime rate, except for Manhattan.Middle-income boroughs are associated with lower crime rate.


###Investigation of Offense Type

```{r,  echo = FALSE}

crime_words = nyc_crime_2017 %>%
  select(-longitude, -latitude) %>%
  mutate(ofns_desc = str_to_lower(ofns_desc),
         ofns_desc = str_replace(ofns_desc, "[2-3]",""),
  ofns_desc = as.character(ofns_desc)) %>%
  unnest_tokens(word, ofns_desc)

data(stop_words)

crime_word_tidy = 
  anti_join(crime_words, stop_words)


crime_word_tidy %>% 
  count(word, sort = TRUE) %>% 
  top_n(10) %>% 
  mutate(word = fct_reorder(word, n)) %>% 
  ggplot(aes(x = word, y = n)) + 
  geom_bar(stat = "identity", fill = "blue", alpha = .6) + 
  coord_flip()+ ggtitle("Top 10 Words in Offense Type")
```


* Top 10 words showing in offense description. 
* The most frequent one is larceny, which appears nearly 100000 times. 
* Others include petit, assault and harrassment.

```{r, echo = FALSE}
word_ratios = crime_word_tidy %>%
  filter(ofns_type %in% c("VIOLATION" , "FELONY")) %>%
  count(word, ofns_type) %>%
  group_by(word) %>% 
  filter(sum(n) >= 5) %>%
  ungroup() %>%
  spread(ofns_type, n, fill = 0) %>%
  mutate(
    violation_odds = (VIOLATION + 1) / (sum(VIOLATION) + 1),
    felony_odds = (FELONY + 1) / (sum(FELONY) + 1),
    log_OR = log(felony_odds / violation_odds)
  ) %>%
  arrange(desc(log_OR)) 


word_ratios %>%
  mutate(pos_log_OR = ifelse(log_OR > 0,  "felony_odds >violation_odds" ,"violation_odds > felony_odds")) %>% 
  group_by(pos_log_OR) %>%
  top_n(10, abs(log_OR)) %>%
  ungroup() %>%
  mutate(word = fct_reorder(word, log_OR)) %>%
  ggplot(aes(word, log_OR, fill = pos_log_OR)) +
  geom_col() +
  coord_flip() +
  ylab("log odds ratio (felony_odds/violation_odds)") +
  scale_fill_discrete(name = "") +
  theme(legend.position = "bottom") +
  ggtitle("Distinct Words in Offense Type of Violation and Felony")
```


* Comparison of dinstinct words in offense type of felony and violation. 
* Dinstinct words in felony are larceny, grand and assault.
* Dinstinct words in violation are harrassment, code and administrative.